;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;
;;																		;;
;; 			=============================================				;;
;; 			=		 G.A.M.M.A. THE THING UPDATE 		=				;;
;;			=			  PARTICLES MODULE   			=				;;
;; 			=============================================				;;
;;																		;;
;; Define your own feedback particle effects here.						;;
;; 		(Or be based and DLTX your effects file)						;;
;;																		;;
;; - Supports layered effects. Up to 10 layers.							;;
;; - Pick random effects separated by commas in the same layer.			;;
;; - If the script can't load the particles it won't crash.				;;
;;																		;;
;; NAMING CONVENTION:													;;
;; [pfx_stalker_(npc section)] for character specific particles.		;;
;; [pfx_monster_(monster section)] same but for monsters.				;;
;; [pfx_faction_(faction name)] for faction specific particles.			;;
;;																		;;
;; EXTRA DOCUMENTATION:													;;
;; - align: Makes the effect face the actor.							;;
;; - ignore_bone: Makes the effect appear at the victim's feet.			;;
;;																		;;
;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;

[pfx_stalker_monolith_eidolon]
layer_1		= anomaly2\gravi_anomaly_shield_00

[pfx_stalker_sim_default_phantom_1]
layer_1		= anomaly2\anomaly_entrance
align		= 1

[pfx_stalker_sim_default_phantom_2]:pfx_stalker_sim_default_phantom_1
[pfx_stalker_sim_default_phantom_3]:pfx_stalker_sim_default_phantom_1

[pfx_stalker_kat_greh_sabaoth]
layer_1		= anomaly2\electra_entrance_small

[pfx_stalker_gen_greh_sabaoth]:pfx_stalker_kat_greh_sabaoth
[pfx_stalker_sar_greh_sabaoth]:pfx_stalker_kat_greh_sabaoth
[pfx_stalker_lab_greh_sabaoth]:pfx_stalker_kat_greh_sabaoth
[pfx_stalker_greh_castigator_1]:pfx_stalker_kat_greh_sabaoth
[pfx_stalker_greh_castigator_2]:pfx_stalker_greh_castigator_1
[pfx_stalker_greh_castigator_3]:pfx_stalker_greh_castigator_1
[pfx_stalker_greh_castigator_4]:pfx_stalker_greh_castigator_1
[pfx_stalker_greh_castigator_5]:pfx_stalker_greh_castigator_1
[pfx_stalker_greh_castigator_6]:pfx_stalker_greh_castigator_1
[pfx_stalker_greh_castigator_7]:pfx_stalker_greh_castigator_1

;;;;;;;;;;
;; LTTZ DC
[pfx_stalker_x18_dark_presence]
layer_1		= explosions\effects\expl_hd_handgrenade_05
align		= 1

[pfx_stalker_stalker_stitch_zombied]
layer_1		= monsters\effects\phantom_birth_01
align		= true

[pfx_stalker_stalker_rogue_monolith]:pfx_stalker_stalker_stitch_zombied
[pfx_stalker_stalker_strelok_dark]:pfx_stalker_stalker_stitch_zombied
[pfx_stalker_army_degtyarev_dark]:pfx_stalker_stalker_stitch_zombied

[pfx_stalker_monolith_eidolon_ghost]:pfx_stalker_monolith_eidolon
layer_2		= monsters\effects\phantom_birth_01

[pfx_stalker_greh_sabaoth_ghost]:pfx_stalker_kat_greh_sabaoth
layer_2		= monsters\effects\phantom_birth_01
;;
;;;;;;;;;


[pfx_faction_greh]
layer_1		= monsters\effects\bloodsucker_trail
layer_2		= monsters\effects\polter_trails_02
layer_3		= anomaly2\effects\bloodsucker_shleyf


;; These are hardcoded and not dynamically read by the script.
[pfx_armor]	;; << When the bullet doesn't penetrate the armor
layer_1		= hit_fx\hit_metal_00, hit_fx\hit_metal_01, hit_fx\hit_metal_02, hit_fx\hit_metal_03
align		= 1

[pfx_flesh]	;; << When the bullet penetrates the armor
layer_1		= anomaly2\effects\gravity_damage_02_blood2
align		= 1

[pfx_gibs]	;; << When you deal excessive amounts of damage
layer_1		= anomaly2\body_tear_00, anomaly2\body_tear_01, anomaly2\body_tear_02
ignore_bone	= 1